MATH 245 Homework 3

### 2024-03-05 PDEs/math245_hw3.Rmd
math hw3, kelp stuff

---
title: "MATH 245 Homework 3"
author: "Ruby Krasnow and Tommy Thach"
date: "2024-02-27"
output:
  pdf_document:
    extra_dependencies: ["derivative", "tcolorbox", "xcolor"]
---

@@

We can see that the first term on the right-hand side is the solution to $(vx)_t = k(vx)_{xx}, -\infty<x<\infty$ with the initial condition $v_x(x, 0) = f'(x)$, i.e., it equals $v_x$. Thus, we can subtract $v_x$ from both sides of the above equation and divide by $-2$ to find show that $(\ast)$ is indeed satisfied by
$$v(x,t)= \frac{1}{\sqrt{4 \pi kt}} \int_{-\infty}^{\infty} e^{-(x-y)^2/4kt}f(y)\;dy, \quad x>0 $$

>>>>

---
title: "MATH 245 Homework 3"
author: "Ruby Krasnow and Tommy Thach"
date: "2024-03-01"
output:
  pdf_document:
    extra_dependencies: ["derivative", "tcolorbox", "xcolor"]
---

@@

We can see that the first term on the right-hand side is the solution to $(v_x)_t = k(v_x)_{xx}, -\infty<x<\infty$ with the initial condition $v_x(x, 0) = f'(x)$, i.e., it equals $v_x$. Thus, we can subtract $v_x$ from both sides of the above equation and divide by $-2$ to find show that $(\ast)$ is indeed satisfied by
$$v(x,t)= \frac{1}{\sqrt{4 \pi kt}} \int_{-\infty}^{\infty} e^{-(x-y)^2/4kt}f(y)\;dy, \quad x>0 $$
